### 2018-04-25 Physics Notes/Turning Points/Overall Notes/Turning Points.tex
Notes update
Notes Update

>>>>

\section{Microscopes}
To find the voltage required to produce electrons of a given wavelength, rearrange the equation on the formula book
$$\lambda=\frac{h}{\sqrt{2meV}}\Rightarrow \ V=\frac{h^2}{2me\lambda^2}$$
\subsection{Transmission electron microscope}
\includegraphics[width=8cm]{tem.png}
This involves firing a beam of electrons at a high voltage towards an ultra thin specimen.\\
When an electron wave encounters the specimen it can either:
\item Pass straight through the specimen without interacting
\item Get absorbed
\item Diffract
The image detail can be improved by increasing the anode voltage of the electron gun.\\
Image detail may reduce when travelling through the specimen as some electrons lose speed.
\subsection{Scanning Tunnelling Microscope}
\includegraphics[width=6cm]{stm.png}
This has a very fine conducting probe very close to the surface of the sample.
